Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-06 manuscript/manuscript.Rmd
added a bit RL

Your text comes here. Separate text sections with \cite{Mislevy06Cog}.

# Section title {#sec:1}

Text with citations by \cite{Galyardt14mmm}.

@@

\begin{align}
a^2+b^2=c^2
\end{align}

>>>>

<!-- Your text comes here. Separate text sections with \cite{Mislevy06Cog}. -->

# Reinforcement learning {#sec:DRL}

Reinforcement learning (RL) is a way of approaching *control problems* through machine learning.
An RL application can be conceptually separated into two parts: an *agent*, and an *environment*.
The agent may *act* on the environment.
This produces two effects: on the one hand, the state of the environment is changed, and on the other, the agent receives a *reward* (see Fig. ).
The reward depends on what action the agent chose, and on the initial and final states of the environment.
The reward encodes the goal which we desire the agent to acheive---in other words, it encodes how we wish the agent controls the environment.
The main part of any RL algorithm is then to progressively improve the agent's *policy*, the function the agent uses to choose which action to take given the state of the environment.
This is done by aggregating experience and learning from it.

# Sustainable fishery management {#sec:fishery}

# Results

# Discussion

<!-- Text with citations by \cite{Galyardt14mmm}.

@@

\begin{align}
a^2+b^2=c^2
\end{align} -->
